Parsing Postfix Log Files

### 2009-04-15 doc/logparser.tex
Changed title page, added declaration and acknowledgements pages.

% $Id$
\documentclass[a4paper,12pt,draft]{report}
\pagestyle{headings}

@@

@@

\title{Parsing Postfix Log Files}
\author{John Tobin \\ School of Computer Science and Statistics \\
Trinity College \\ Dublin 2 \\ Ireland \\ tobinjt@cs.tcd.ie}
\maketitle

@@

    \setcounter{page}{2}
    \phantomsection{}
    \addcontentsline{toc}{chapter}{Abstract}

    Parsing Postfix log files is much more difficult than it first appears,
    but it \textit{is\/} possible to achieve a high degree of accuracy in
    understanding Postfix log files, and subsequently in reconstructing the
    actions taken by Postfix when processing mail delivery attempts.  This
    thesis describes the creation of a parser for Postfix log files,
    documenting the architecture developed for this project and the parser
    that implements it, explaining the difficulties encountered and the
    solutions developed, with reference to an implementation that stores
    data gleaned from the log files in an SQL database.  The gathered data
    can be used to optimise current anti-spam measures, to produce
    statistics showing how effective those measures are, or to provide a
    baseline to test new anti-spam measures against.  The Postfix log file
    parser needs to be very precise and strict when parsing log files, yet
    must allow users to easily adapt or extend it to parse new log lines,
    without requiring that the user have an in-depth knowledge and
    understanding of the parser's internal workings.  The newly developed
    architecture is designed to make the process of parsing new inputs as
    simple as possible, enabling users to trivially add new rules (to parse
    variants of known inputs) and relatively easily add new actions (to
    process a previously unknown category of inputs).  The architecture
    scales linearly or better as the number of rules and size of input
    increases, making it suitable for parsing large corpora or months of
    accumulated data.

@@

    XXX MAIL MADS ABOUT EXAMINERS\@.

@@

@@

\setcounter{page}{3}
\tableofcontents
\listoffigures
\listoftables

>>>>

% $Id$
\documentclass[a4paper,12pt,draft]{report}

@@

\newcommand{\specialpage}[1]{%
    \phantomsection{}
    \addcontentsline{toc}{chapter}{#1}%
}
\newcommand{\specialpageheading}[1]{%
    \begin{center}
        \textbf{\Large #1}
    \end{center}
}
\newcommand{\specialpageandheading}[1]{%
    \specialpage{#1}
    \specialpageheading{#1}
}

@@

\pagestyle{empty}

\specialpage{Title}

\begin{center}

    {\Huge Parsing Postfix Log Files}

    \vfill{}

    {\LARGE John Tobin}

    \vfill{}

    A thesis submitted to the University of Dublin, in fulfilment of the
    requirements for the degree of Master of Science in Computer Science.

    \vfill{}

    April 2009

    \vfill{}

    \vfill{}

    \vfill{}

\end{center}

\newpage{}

% Declaration
\specialpageandheading{Declaration}

\vfill{}

\noindent{}I declare that this thesis, and the work described herein, is
entirely my own work, and has not been submitted as an exercise for a
degree at this or any other university.  This thesis may be borrowed or
copied upon request with the permission of the Librarian, Trinity College,
University of Dublin.

\vfill{}

\begin{flushright}
    \underline{\hspace*{10em}} \\~\\
    John Tobin \\
    \today{}
\end{flushright}

\vfill{}

\vfill{}

\vfill{}

\vfill{}

\newpage{}

% Acknowledgements
\specialpageandheading{Acknowledgements}

\noindent{}I would like to express my appreciation to my supervisor, Dr.\
Carl Vogel, for his advice, assistance, and guidance.

\bigskip{}

\noindent{}I would like to thank my wife, Ariane Tobin, for her patience,
good will, and encouragement.

@@

    \setcounter{page}{4}
    \phantomsection{}
    \addcontentsline{toc}{chapter}{Abstract}

    Parsing Postfix log files is much more difficult than it first appears,
    but it \textit{is\/} possible to achieve a high degree of accuracy in
    understanding Postfix log files, and subsequently in reconstructing the
    actions taken by Postfix when processing mail delivery attempts.  This
    thesis describes the creation of a parser for Postfix log files,
    documenting the architecture developed for this project and the parser
    that implements it, explaining the difficulties encountered and the
    solutions developed, with reference to an implementation that stores
    data gleaned from the log files in an SQL database.  The gathered data
    can be used to optimise current anti-spam measures, to produce
    statistics showing how effective those measures are, or to provide a
    baseline to test new anti-spam measures against.  The Postfix log file
    parser needs to be very precise and strict when parsing log files, yet
    must allow users to easily adapt or extend it to parse new log lines,
    without requiring that the user have an in-depth knowledge and
    understanding of the parser's internal workings.  The newly developed
    architecture is designed to make the process of parsing new inputs as
    simple as possible, enabling users to trivially add new rules (to parse
    variants of known inputs) and relatively easily add new actions (to
    process a previously unknown category of inputs).  The parser
    implemented for this project is evaluated on the criteria of efficiency
    and coverage of Postfix log files, demonstrating that the conflicting
    goals of efficiency and accuracy can be balanced, and one need not be
    sacrificed to achieve the other.

@@

@@

% Include the header across the top of each page, after the declaration.
\pagestyle{headings}

@@

\setcounter{page}{5}
\tableofcontents
\listoffigures
\listoftables
